An Empirical Analysis of the Role of Energy in Economic Growth

### 2014-06-19 Article/EconGrowth2.Rnw
Adding section on future work.
Added paragraph on energy quantifications.

>>>>

In the future, we intend add an additional coordinate of analysis 
(Section~\ref{sec:Coordinates}):
energy quantification.
We wish to include exergy ($X$) and useful work ($U$) energy quantifications
in the economic models.
Doing so will provide an opportunity to engage the 
literature around useful work as a driver 
of economic growth.\citep{Ayres:2003ec, Ayres:2005kn, Ayres:2010ug, 
Warr:2006hc, Warr:2010ga, Warr:2010ht, Warr:2012cg}
And, we will be able to assess whether any models provide better 
descriptions of economic growth with a given energy quantification.
We intend to look at additional countries as data becomes available
for the various enegy quantifications.
And, we wish to look over longer time scales.
In particular, we wish to investigate the effects of significant 
processes (such as industrialization) and events (world wars)
using the resampling techniques presented herein.
